A Stochastic Quasi-Newton Optimizer for TensorFlow

### 2018-05-07 paper/main.tex
Final commit...?

\begin{abstract}
  We do some shit and it doesn't work.
\end{abstract}

@@

\begin{enumerate}
  \item Review main results of the Wang, Ma, Goldfarb, Liu paper
    \cite{sdlbfgs}
  \item State the SdLBFGS algortihm.
  \item Mention some details about how the algorithm translates to code.
\end{enumerate}

@@

We evaluate our implementation of SdLBFGS on a collection of test functions.
Figure \ref{fig:convex-linear-system} shows the effect of changing the memory
capacity on a relatively small fully-observable convex differentiable problem.
Figure \ref{fig:nonconvex-comparison}.

@@

>>>>

\begin{abstract}
  We implement a stochastic damped limited memory version of the classical BFGS
  quasi-Newton minimization algorithm for use in the \texttt{TensorFlow}
  graphical computation and neural network framework. The implementation is
  linked to \texttt{TensorFlow} as an \texttt{ExternalOptimizerInterface}
  object, which circumvents architectural challenges in implementing
  second-order methods. We provide empirical data to show that the
  implementation can solve minimization problems in line with its peers. We do
  not report results on typical problems that are solved using
  \texttt{TensorFlow} because we find problems of this scale are presently
  computationally intractible for our implementation.
\end{abstract}

@@

% \begin{enumerate}
%   \item Review main results of the Wang, Ma, Goldfarb, Liu paper
%     \cite{sdlbfgs}
%   \item State the SdLBFGS algortihm.
%   \item Mention some details about how the algorithm translates to code.
% \end{enumerate}

@@

We evaluate our implementation of SdLBFGS on a collection of test functions.
Figure \ref{fig:convex-linear-system} shows the effect of changing the memory
capacity on a relatively small fully-observable convex differentiable problem.
Figure \ref{fig:nonconvex-comparison}. Additionally, we compare the performance
of our implementation of SdLBFGS with other common minimizers on a
dataset\footnote{The data was provided by Professor Orabona.} for a Higgs boson
classification problem. Empirical results in Figure \ref{fig:svm-hinge} are
interesting simply by virtue of lacking any theoretical justification for
convergence, as the loss function is not $C^1$ with Lipschitz gradient. The
results when the loss function is in $C^1$ with Lipschitz gradient, as in Figure
\ref{fig:svm-tan}, however, do conform to the theoretical guarantees.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{../plots/svm_hinge_loss.eps}
  \caption{
    SdLBFGS performance on the Higgs boson dataset using an SVM classifier with
    a hinge loss function, compared with other minimization algorithms. Though
    no theoretical guarantees are made about the performance of SdBFGS, we
    observe that it behaves quite well with respect to its peers. The outlier
    performance is the standard L-BFGS algorithm, which seems to behave poorly
    on this problem.
  }
  \label{fig:svm-hinge}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{../plots/svm_tan_regularized_loss.eps}
  \caption{
    SdLBFGS performance on the Higgs boson dataset using an SVM classifier with
    a smooth regularized function, compared with other minimization algorithms.
    Unlike in Figure \ref{fig:svm-hinge}, we do have theoretical convergence
    guarantees for this $f(x)$. We also
    observe that it behaves quite well with respect to its peers. The outlier
    performance is again the standard L-BFGS algorithm, which seems to behave poorly
    on this problem.
  }
  \label{fig:svm-tan}
\end{figure}
